Lay Perceptions of Crowd-Scientific Findings: The Risks of Variability and Lack of Consensus

### 2021-10-10 manuscript/manuscript.Rmd
improvements figures (fonts, sizes), small edits talk+poster

p1 <- ggplot(mapping = aes(x = term, 
                           y = estimate,
                           color = Conclusion), 
             data = tidy_results) +
  geom_point(size = 2) +
  geom_errorbar(mapping = aes(ymin = conf.low, ymax = conf.high), 
                size = 0.8, width = 0.2) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray34", alpha = 0.7) +
  facet_wrap(~ Measure, 
             labeller = labeller(Measure = Measure.label)) + 
  theme_bw() + 
  theme(strip.background = element_rect(fill = "white"),
        legend.position = "",
        text = element_text(size = 16)) +
  labs(x = "Condition", y = "Estimate and 95% Confidence Interval") +
   scale_x_discrete(labels = c("Multi-\nconsistent", "Multi-\ninconsistent"))  +
  scale_color_discrete(type = c("darkgrey", "red", "green4"))

ggsave("Figure1.jpg", p1, 
       width = 7, height = 5, units = "in")

@@

colors <- rep(c("#2142d9", "darkorange"), 3) #choose colors

@@

  annotate(geom = "text", 
           label = "Single-analyst", 
           x = 3.8, y = 12, size = 6) + 
  annotate(geom = "text", 
           label = "Multi-consistent", 
           x = 2.7, y = 14, size = 6) + 
  annotate(geom = "text", 
           label = "Multi-inconsistent",
           x = 1.75, y = 16, size = 6) + 
  annotate(geom = "text", 
           label = "Prior Beliefs", 
           x = 4.2, y = 20, size = 10, 
           color = "#2142d9") + 
  annotate(geom = "text", 
           label = "vs.", 
           x = 4.2, y = 45, size = 10) + 
  annotate(geom = "text", 
           label = "Posterior Beliefs", 
           x = 4.2, y = 75, size = 10, 
           color = "darkorange") +

  theme_classic() +
  theme(axis.ticks.y = element_blank(),
        #axis.text = element_text(size = 9),
        axis.title.y = element_blank(),
        text = element_text(size = 20))

ggsave("Figure2.jpg", p2, 
       width = 7, height = 5, units = "in")

>>>>

p1 <- ggplot(mapping = aes(x = term, 
                           y = estimate,
                           color = Conclusion), 
             data = tidy_results) +
  geom_point(size = 2) +
  geom_errorbar(mapping = aes(ymin = conf.low, ymax = conf.high), 
                size = 0.8, width = 0.2) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray34", alpha = 0.7) +
  facet_wrap(~ Measure, 
             labeller = labeller(Measure = Measure.label)) + 
  theme_bw() + 
  theme(strip.background = element_rect(fill = "white"),
        legend.position = "",
        text = element_text(size = 16, 
                            family = "serif")) +
  labs(x = "Condition", y = "Estimate and 95% Confidence Interval") +
   scale_x_discrete(labels = c("Multi-\nconsistent", "Multi-\ninconsistent"))  +
  scale_color_discrete(type = c("darkgrey", "red", "green4"))

ggsave("Figure1.jpg", p1, 
       width = 7, height = 5, units = "in") #save to manuscript folder

ggsave(paste0(here(), "/talk/images/Figure1.jpg"), p1, 
       width = 7, height = 5, units = "in") #save to talk folder

ggsave(paste0(here(), "/poster/Figure1.jpg"), p1, 
       width = 7, height = 5, units = "in") #save to poster folder

@@

colors <- rep(c("#035AA6", "darkorange"), 3) #choose colors

@@

  annotate(geom = "text", 
           label = "Single-analyst", 
           x = 3.8, y = 13, size = 6,
           family = "serif") + 
  annotate(geom = "text", 
           label = "Multi-consistent", 
           x = 2.73, y = 14, size = 6,
           family = "serif") + 
  annotate(geom = "text", 
           label = "Multi-inconsistent",
           x = 1.78, y = 16, size = 6,
           family = "serif") + 
  annotate(geom = "text", 
           label = "Prior Beliefs", 
           fontface = "bold",
           x = 4.2, y = 26, size = 8, 
           color = "#035AA6",
           family = "serif") + 
  annotate(geom = "text", 
           label = "vs.", 
           x = 4.2, y = 45, size = 8,
           family = "serif") + 
  annotate(geom = "text", 
           label = "Posterior Beliefs", 
           fontface = "bold",
           x = 4.2, y = 68, size = 8, 
           color = "darkorange",
           family = "serif") +

  theme_classic() +
  theme(axis.ticks.y = element_blank(),
        #axis.text = element_text(size = 9),
        axis.title.y = element_blank(),
        text = element_text(size = 16, family = "serif"))

ggsave("Figure2.jpg", p2, 
       width = 7, height = 5, units = "in") #save to manuscript folder

ggsave(paste0(here(), "/talk/images/Figure2.jpg"), p2, 
       width = 7, height = 5, units = "in") #save to talk folder

ggsave(paste0(here(), "/poster/Figure2.jpg"), p2, 
       width = 7, height = 5, units = "in") #save to poster folder

### 2021-10-10 poster/GSPA_Poster.Rmd
improvements figures (fonts, sizes), small edits talk+poster

---
title: |
  | Lay Perceptions of Scientific Findings:
  | The Risks of Variability and Lack of Consensus
author:
  - name: Insert first author name here 
    affil: 1
    orcid: ''
  - name: Insert second author name here
    affil: 1
affiliation:
  - num: 1
    address: Insert affiliation here
column_numbers: 3
#logoright_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
#logoleft_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
output: 
  posterdown::posterdown_html:
    self_contained: true
    css: style.css
knit: pagedown::chrome_print
font_family: 'Cabin'
titletext_fontfamily: 'Cabin'
primary_colour: "#035AA6"
accent_colour: "#035AA6"
sectitle2_textcol: "#035AA6"
header-includes:
  - \setlength{\parindent}{4em}
  - \setlength{\parskip}{0em}
---

@@

```{r, echo = FALSE, out.width='101%', fig.retina=3, fig.align='left'}
knitr::include_graphics("mermaid.png")
```

@@

**Figure 1**: *Estimates (and 95% CIs) for all outcomes*

```{r, echo = FALSE, out.width='90%', fig.retina=3, fig.align='left'}
knitr::include_graphics("Figure1.jpg")
```

**In line with our hypotheses**, lay consumers of multi-analyst studies with **inconsistent** results  
`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~~$ Have lower posterior beliefs  
`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~~$ Find the results less credible  
`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~~$ Have less confidence in the average effect size estimate  
`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the results are more likely to stem from bias  
`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the results are more likely to stem from error

@@

# Discussion  
**Conclusions**  
`r icon_style(icons::fontawesome("sitemap"), scale = 1.4, fill = "#035AA6")` $~$ Crowdsourced data analysis has **many worthy uses**, but...    
`r icon_style(icons::fontawesome("exclamation-triangle"), scale = 1.4, fill = "#035AA6")` $~~$ **Variability** and  **lack of consensus** may evoke negative responses

>>>>

---
title: |
  | Lay Perceptions of Scientific Findings:
  | The Risks of Variability and Lack of Consensus
author:
  - name: Insert first author name here 
    affil: 1
    orcid: ''
  - name: Insert second author name here
    affil: 1
affiliation:
  - num: 1
    address: Insert affiliation here
column_numbers: 3
#logoright_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
#logoleft_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
output: 
  posterdown::posterdown_html:
    self_contained: true
    css: style.css
knit: pagedown::chrome_print
font_family: 'Cabin'
titletext_fontfamily: 'Cabin'
primary_colour: "#035AA6"
accent_colour: "#035AA6"
sectitle2_textcol: "#035AA6"
---

@@

```{r, echo = FALSE, out.width='100%', fig.retina=3, fig.align='left'}
knitr::include_graphics("mermaid.png")
```

@@

**Figure 1**: *Estimates (and 95% CIs) for all outcomes*
```{r, echo = FALSE, out.width='95%', fig.retina=3, fig.align='left'}
knitr::include_graphics("Figure1.jpg")
```
**In line with our hypotheses**, lay consumers of multi-analyst studies with **inconsistent** results  
`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~~$ Have lower posterior beliefs  
`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~~$ Find the results less credible  
`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~~$ Have less confidence in the average effect size estimate  
`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the results are more likely to stem from bias  
`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the results are more likely to stem from error

@@

# Discussion  
**Conclusion**  
`r icon_style(icons::fontawesome("sitemap"), scale = 1.4, fill = "#035AA6")` $~$ Crowdsourced data analysis has **many worthy uses**, but...    
`r icon_style(icons::fontawesome("exclamation-triangle"), scale = 1.4, fill = "#035AA6")` $~~$ **Variability** and  **lack of consensus** may evoke negative responses

### 2021-10-10 talk/index.Rmd
poster: first draft, manuscript+talk: improved figures (greater fonts, color for results), small changes in text
improvements figures (fonts, sizes), small edits talk+poster

title_plot <- ggplot(data = estimates, 
                     mapping = aes(x = Team, y = Estimate, color = Conclusion)) +
  geom_point(size = 2) +
  geom_errorbar(mapping = aes(ymin = Estimate - 1.96 * se, 
                              ymax = Estimate + 1.96 * se),
                width = 3) + 
  theme_classic() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey") +
  labs(x = "Science Team", 
       y = "Obtained Effect Size",
       color = "Conclusion of Science Team") +
  scale_color_discrete(type = c("red", "orange", "green4")) +
  theme(legend.position = c(0.35, 0.8),
        text = element_text(size = 19))

@@

$~~$  
and study the **effects on**

@@

`r icon_style(icons::fontawesome("route"), scale = 1.5, fill = "#035AA6")`   $~~~$ Crowdsourced data analysis has **many worthy uses**  
--

@@

`r icon_style(icons::fontawesome("users-slash"), scale = 1.4, fill = "#035AA6")` $~~$ Do lay consumers respond negatively to **variability** and  **lack of consensus**?   
--

>>>>

title_plot <- ggplot(data = estimates, 
                     mapping = aes(x = Team, y = Estimate, color = Conclusion)) +
  geom_point(size = 2) +
  geom_errorbar(mapping = aes(ymin = Estimate - 1.96 * se, 
                              ymax = Estimate + 1.96 * se),
                width = 3) + 
  theme_classic() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey") +
  labs(x = "Science Team", 
       y = "Obtained Effect Size",
       color = "Conclusion of Science Team") +
  scale_color_discrete(type = c("red", "orange", "green4")) +
  theme(legend.position = c(0.35, 0.8),
        text = element_text(size = 20, family = "serif"))

@@

$~~$  
In all three conditions, the given estimates average to 5%. We study the **effects on**

@@

`r icon_style(icons::fontawesome("sitemap"), scale = 1.5, fill = "#035AA6")`   $~$ Crowdsourced data analysis has **many worthy uses**  
--

@@

`r icon_style(icons::fontawesome("users-slash"), scale = 1.4, fill = "#035AA6")` $~~$ Lay consumers may respond negatively to **variability** and  **lack of consensus**   
--
